Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-04-04 doc/Papers/IQS_convergence/IQS_convergence.tex
Adding acknowlegments section

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This work was supported by the Department of Energy, Idaho National Laboratory, and the Integrated University Program Fellowship.  We thank Mark Dehart, Yaqi Wang, the NEAMS program, and INL's MOOSE/Rattlesnake team for their support. This research did not receive any specific grant from funding agencies in the public, commercial, or
not-for-profit sectors.
